---
title: "block3"
author: "Ankur Shrivastava"
date: "27 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Block 3 Data Analysis

```{r pl1}

library(dplyr)
library(lubridate)
library(ggplot2)
library(plotly)
library(pander)

block3 <- read.csv("users_pw_anm_block3.csv", stringsAsFactors = FALSE, 
                   na.strings=c("NULL","NULL "," NULL ","NA"," ","", "-1"))
str(block3)

```
## ----------Data Cleaning and preparation--------------------------------

```{r bl2}
block3$user_id <- as.numeric(block3$user_id)

#Following variables represent categories and not character or intgers
categorical <- c("user_type", "user_sex", "user_acc_status", "pw_profile_bpl_card", "pw_profile_edu", "pw_profile_type_uid",
                 "pw_profile_first_preg", "pw_profile_birth_order", "pw_profile_prev_pih",
                 "pw_profile_prev_sb", "pw_profile_prev_low_wt", "pw_profile_prev_miscarriage",
                 "pw_profile_prev_c_section", "pw_profile_prev_pph", "pw_profile_heart_disease",
                 "pw_profile_thyroid_disease", "pw_profile_epilepsy", "pw_profile_reproductive_surg",
                 "pw_profile_other_flag", "pw_profile_family_diabetes", "pw_profile_family_pih",
                 "pw_profile_multi_preg", "pw_profile_blood_group", "pw_profile_hiv")

#Converting to categorical variables
block3[, categorical] <- lapply(block3[, categorical], as.factor)
str(block3[, categorical])

```


Following are date variables and should be changed to date

```{r bl3}
datevars <- c("pw_profile_dob", "pw_profile_lmp", "pw_profile_edd")

block3[, datevars] <- lapply(block3[, datevars], ymd)

str(block3[, datevars])

```

```{r bl4}
#Following are datetime variables and should be changed to datetime
datetimevars <- c("registeration_date", "last_login_time", "pw_profile_form_start_time", "pw_profile_form_fill_time",
                  "pw_profile_reg_date")

block3[, datetimevars] <- lapply(block3[, datetimevars], ymd_hms)
str(block3[, datetimevars])
```

Line Plot for number of records by each user
```{r bl5}
agg_user <- block3 %>% group_by(user_id) %>% tally()

usr_lines <- ggplot(agg_user, aes(x = user_id, y = n)) + 
                 geom_line() + xlab("User Id") + ylab("Number of Records")

ggplotly(usr_lines)
```
Point Plot for number of records by each user

```{r bl6}
#Aggregate number of records by each user
usr_points <- ggplot(agg_user, aes(x = user_id, y = n)) + 
                  geom_point() + xlab("User Id") + ylab("Number of Records")

ggplotly(usr_points)
```
Form filling trend

```{r bl6-a}
block3$anm_visit_detail_form_fill_date <- as.Date(block3$anm_visit_detail_form_fill_time)

#Form filling trend by each user
agg_user_date <- block3 %>% group_by(user_id, anm_visit_detail_form_fill_date) %>% tally()

agg_user_date <- agg_user_date[!is.na(agg_user_date$anm_visit_detail_form_fill_date),]

usrid <- sort(unique(na.omit(agg_user_date$user_id)))

#Show form filling trend for each of the users
for(i in usrid){
  plot <- ggplot(agg_user_date[agg_user_date$user_id == i, ], aes(x = anm_visit_detail_form_fill_date, y = n)) +
    geom_point() + xlab("Date") + ylab("Number of records") +
    ggtitle(paste("User id", as.character(i)))
  print(plot)
}

```
Aggregate values
```{r bl7}
#Aggregate values by each subcenter
agg_subcent <- block3 %>% group_by(subcenter_id) 


subcent <- sort(unique(na.omit(agg_subcent$subcenter_id)))
```
Systolic BP values 

```{r bl8}
#Show systolic bp values in each of the subcenters
for(i in subcent){
 plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x =      pw_profile_id, y = anm_visit_detail_bp_sys)) +
    geom_point() + xlab("Pw Profile Id") + ylab("Blood Pressure Systolic") +
    ggtitle(paste("Subcenter", as.character(i)))

# plot <-plot_ly(data = agg_subcent[agg_subcent$subcenter_id == i, ], x = pw_profile_id,y = anm_visit_detail_bp_sys,type='scatter',mode='markers')
# 
# #defining labels and titile using layout()
# layout(plot,title = paste("Subcenter", as.character(i)),
#        xaxis = list(title = "Pw Profile Id"),
#        yaxis = list(title = "Blood Pressure Systolic"))
 print(plot)

}

```
Diastolic BP values

```{r bl9}
#Show diastolic bp values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_bp_dia)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("Blood Pressure Diastolic") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}
```
Pulse values

```{r bl10}
#Show pulse values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_pulse)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("Pulse rate") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}
```
Weight values

```{r bl11}
#Show weight values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_weight)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("Weight") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}
```
Height values
```{r bl12}
#Show height values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_height)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("Height") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}
```
BMI values

```{r bl13}
#Show bmi values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_bmi)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("BMI") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}
```
Temperature Values

```{r bl14}
#Show temperature values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_temp)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("Temperature") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}
```
Haemoglobin Count

```{r bl15}
#Show Haemoglobin count values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_hb)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("Hb count") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}
```
Fetal bpm

```{r bl16}
#Show Fetal bpm values in each of the subcenters
for(i in subcent){
  plot <- ggplot(agg_subcent[agg_subcent$subcenter_id == i, ], aes(x = pw_profile_id, y = anm_visit_detail_fetal_bpm)) + 
    geom_point() + xlab("Pw Profile Id") + ylab("Fetal bpm") +
    ggtitle(paste("Subcenter", as.character(i)))
  print(plot)
}

#---------------------------------------------------------------------------
```
